MS Depression Paper

### 2022-08-23 msdepression/scripts/MS_Depression_First_Paper_started_20220728/msdepression_n380_started_20220728.Rmd
added t tests
including wilcoxon tests

@@

@@

sorted_ggplot<-ggplot(data = fascicle_values_sorted_by_overlap, aes(x = fascicle, y=value, fill=value))+
  ggtitle("Volume per Fascicle Affected Nondepressed, exclude CC") + 
  ylab("Volume") + 
  geom_bar(stat="identity") + 
  scale_fill_continuous(type="viridis") + 
  ylim(0,30000) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5, size=14),
        axis.title.x = element_text(size=14),
        axis.title.y = element_text(size=14),
        axis.line = element_line(size=1),
        panel.background = element_rect(colour = "white", fill = "white"))
print(sorted_ggplot)

@@

sorted_ggplot<-ggplot(data = fascicle_values_sorted_by_overlap, aes(x = fascicle, y=value, fill=value))+
  ggtitle("Volume per Fascicle Affected Depressed, exclude CC") + 
  ylab("Volume") + 
  geom_bar(stat="identity") + 
  scale_fill_continuous(type="viridis") + 
  ylim(0,30000) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5, size=14),
        axis.title.x = element_text(size=14),
        axis.title.y = element_text(size=14),
        axis.line = element_line(size=1),
        panel.background = element_rect(colour = "white", fill = "white"))
print(sorted_ggplot)
```

@@

@@

@@

violin_mean_fascicle_volume_dep <- ggplot(df_mean_fascicle_volumes_and_diagnosis, aes(x=depGroupVar, y=total_fascicle_vol_lost_indepnet_top_quartile, fill=depGroupVar)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  scale_x_discrete(labels=c("1" = "Depressed", "2" = "Non-Depressed")) + 
  ggtitle(paste0("Mean Fascicle Volume Affected Dep Net by Diagnosis")) +
  ylab("Mean Volume of Fascicles") +
  ylim(0,42000) + 
  theme(plot.title = element_text(size=16, hjust = 0.55),
        axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
        axis.title.y = element_text(size=16),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
        legend.position = "none",
        aspect.ratio=7/5,
        panel.background = element_rect(colour = "white", fill = "white"))
print(violin_mean_fascicle_volume_dep) #p=0.067

violin_mean_fascicle_volume_nondep <- ggplot(df_mean_fascicle_volumes_and_diagnosis, aes(x=depGroupVar, y=total_fascicle_vol_lost_nondep_bottom_3_quartiles,  fill=depGroupVar)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  scale_x_discrete(labels=c("1" = "Depressed", "2" = "Non-Depressed")) + 
  ggtitle(paste0("Mean Fascicle Volume Affected Nondep Net by Diagnosis")) +
  ylab("Mean Volume of Fascicles") +
  ylim(0,42000) + 
  theme(plot.title = element_text(size=16, hjust = 0.55),
        axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
        axis.title.y = element_text(size=16),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
        legend.position = "none",
        aspect.ratio=7/5,
        panel.background = element_rect(colour = "white", fill = "white"))
print(violin_mean_fascicle_volume_nondep) 
```

@@

>>>>

dep_network_total_volume_top_quartile_no_cranial_nerves <-
sum(fascicle_volumes_dep_network$num_voxels_total[which(fascicle_volumes_dep_network$fascicle %in% dep_network_names_top_quartile_no_cranial_nerves_by_vol)])

@@

bottom_75_total_volume_no_cranial_nerves <-
sum(fascicle_volumes_dep_network$num_voxels_total[which(fascicle_volumes_dep_network$fascicle %in% dep_network_names_bottom_3_quartiles_no_cranial_nerves_by_vol)])

@@

sorted_ggplot<-ggplot(data = fascicle_values_sorted_by_overlap, aes(x = fascicle, y=value, fill=value))+
  ggtitle("Volume per Fascicle Affected Nondepressed, exclude CC") + 
  ylab("Volume") + 
  geom_bar(stat="identity") + 
  scale_fill_continuous(type="viridis") + 
  ylim(0,30000) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        axis.text.y = element_text(size=12),
        plot.title = element_text(hjust = 0.5, size=14),
        axis.title.x = element_text(size=14),
        axis.title.y = element_text(size=14),
        axis.line = element_line(size=1),
        panel.background = element_rect(colour = "white", fill = "white"))
print(sorted_ggplot)

@@

sorted_ggplot<-ggplot(data = fascicle_values_sorted_by_overlap, aes(x = fascicle, y=value, fill=value))+
  ggtitle("Volume per Fascicle Affected Depressed, exclude CC") + 
  ylab("Volume") + 
  geom_bar(stat="identity") + 
  scale_fill_continuous(type="viridis") + 
  ylim(0,30000) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        axis.text.y = element_text(size=12),
        plot.title = element_text(hjust = 0.5, size=14),
        axis.title.x = element_text(size=14),
        axis.title.y = element_text(size=14),
        axis.line = element_line(size=1),
        panel.background = element_rect(colour = "white", fill = "white"))
print(sorted_ggplot)
```

@@

#isolate out only the depressed group and healthy group, make a column that sums up the total volume loss, only pay attention to places without cranial nerves

### of note, order of operations is that you take the mean first, and then you divide by the total volume of the network. One could imagine a situation where you divide by network first, and then take mean, but it seems reasonable to include network measure after calculating the network mean.

dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicle_volumes_full %>% 
  filter(depGroupVar != 0)  %>% 
  mutate(total_fascicle_vol_lost = rowMeans(across(fascicle_names_no_cranial_nerves))) %>%
  mutate(total_fascicle_vol_lost_indepnet_top_quartile = 
           rowMeans(across(dep_network_names_top_quartile_no_cranial_nerves_by_vol))) %>%
  mutate(prop_fascicle_vol_lost_indepnet_top_quartile = (total_fascicle_vol_lost_indepnet_top_quartile / dep_network_total_volume_top_quartile_no_cranial_nerves)) %>%
  mutate(total_fascicle_vol_lost_nondep_bottom_3_quartiles = 
           rowMeans(across(dep_network_names_bottom_3_quartiles_no_cranial_nerves_by_vol))) %>%
  mutate(total_fascicle_vol_lost_no_cc = rowMeans(across(fascicle_names_no_cranial_nerves[fascicle_names_no_cranial_nerves!="CC"]))) %>%
  mutate(prop_fascicle_vol_lost_bottom_3_quartile = (total_fascicle_vol_lost_nondep_bottom_3_quartiles / bottom_75_total_volume_no_cranial_nerves)) %>%
  mutate(total_fascicle_vol_lost_indepnet_top_quartile_no_cc = 
           rowMeans(across(dep_network_names_top_quartile_no_cranial_nerves_by_vol[dep_network_names_top_quartile_no_cranial_nerves_by_vol != "CC"]))) %>%
  mutate(total_fascicle_vol_lost_nondep_bottom_3_quartiles_no_cc = 
           rowMeans(across(dep_network_names_bottom_3_quartiles_no_cranial_nerves_by_vol[dep_network_names_bottom_3_quartiles_no_cranial_nerves_by_vol != "CC"]))) %>%
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup()

#test whether ms preferentially hits within or outside depression network, p = 2.2 * 10^-16, mean lost in dep net = 18027, mean lost outside dep net = 4020. More disease outside versus inside, when you look at means

msdisease_within_versus_outside_depression_network <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_vol_lost_indepnet_top_quartile, dep_and_healthy_groups_for_ICD_analysis$total_fascicle_vol_lost_nondep_bottom_3_quartiles, var.equal = F, paired = TRUE)

#wilcox test because non normally distributed; p < 2.2*10^-16
msdisease_within_versus_outside_depression_network_wilcoxon <- wilcox.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_vol_lost_indepnet_top_quartile, dep_and_healthy_groups_for_ICD_analysis$total_fascicle_vol_lost_nondep_bottom_3_quartiles,paired = TRUE)

#still 2.2*10^-16; mean of dep net: 6856, mean outside dep net = 4020, excluded corpus callosum b/c it is so very big. 
msdisease_within_versus_outside_depression_network_no_cc <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_vol_lost_indepnet_top_quartile_no_cc, dep_and_healthy_groups_for_ICD_analysis$total_fascicle_vol_lost_nondep_bottom_3_quartiles_no_cc, var.equal = F, paired = TRUE)

#2.2*1^-16
msdisease_within_versus_outside_depression_network_no_cc_wilcoxon <- wilcox.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_vol_lost_indepnet_top_quartile_no_cc, dep_and_healthy_groups_for_ICD_analysis$total_fascicle_vol_lost_nondep_bottom_3_quartiles_no_cc, paired = TRUE)

#testing group differences if you scale by the size of the network, still significant, in top quartile, proportion lost = 0.021
#bottom 3, proportion lost = 0.006, p=2.2 * 10^-16

msdisease_within_versus_outside_depression_network_scaled_by_network_size <- t.test(dep_and_healthy_groups_for_ICD_analysis$prop_fascicle_vol_lost_indepnet_top_quartile, dep_and_healthy_groups_for_ICD_analysis$prop_fascicle_vol_lost_bottom_3_quartile, var.equal = F, paired = TRUE)

#2.2 *10^-16
msdisease_within_versus_outside_depression_network_scaled_by_network_size_wilcoxon <- wilcox.test(dep_and_healthy_groups_for_ICD_analysis$prop_fascicle_vol_lost_indepnet_top_quartile, dep_and_healthy_groups_for_ICD_analysis$prop_fascicle_vol_lost_bottom_3_quartile, paired = TRUE)

#test whether volume lost overall different between depressed and healthy- Yes, p = 0.045, Dep = 9382, Non dep = 8260
total_volume_lost_dep_vs_healthy_unique <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_vol_lost[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$total_fascicle_vol_lost[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], var.equal = F)

#Yes, p=0.046, Dep = 4952, nondep = 4284
total_volume_lost_dep_vs_healthy_unique_no_cc <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_vol_lost_no_cc[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$total_fascicle_vol_lost_no_cc[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], var.equal = F)

#look at within depression network using top quartiles, yes p = 0.034, Dep = 18957, non dep = 16572
total_volume_lost_dep_vs_healthy_unique_in_dep_network_top_quartile <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_vol_lost_indepnet_top_quartile[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$total_fascicle_vol_lost_indepnet_top_quartile[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], var.equal = F)

#no corpus callosum, p = 0.028, Dep = 7380, nondep = 6036
total_volume_lost_dep_vs_healthy_unique_in_dep_network_top_quartile_no_cc <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_vol_lost_indepnet_top_quartile_no_cc[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$total_fascicle_vol_lost_indepnet_top_quartile_no_cc[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], var.equal = F)

#look at bottom 75%, p = 0.07, dep = 4198, non dep = 3740
total_volume_lost_dep_vs_healthy_unique_in_bottom_3_quartiles <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_vol_lost_nondep_bottom_3_quartiles[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$total_fascicle_vol_lost_nondep_bottom_3_quartiles[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], var.equal = F) #mean dep = 30%, mean non_dep = 27%, p = 0.057

#gut check, this should be identical, since CC not in bottom 3 quartiles; p = 0.07, dep = 4198, non dep = 3740
total_volume_lost_dep_vs_healthy_unique_in_bottom_3_quartiles_no_cc <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_vol_lost_nondep_bottom_3_quartiles_no_cc[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$total_fascicle_vol_lost_nondep_bottom_3_quartiles_no_cc[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2], var.equal = F) #mean dep = 30%, mean non_dep = 27%, p = 0.057

@@

df_mean_fascicle_volumes_and_diagnosis_no_cc <- dep_and_healthy_groups_for_ICD_analysis %>% 
dplyr::select(total_fascicle_vol_lost_no_cc, total_fascicle_vol_lost_indepnet_top_quartile_no_cc, total_fascicle_vol_lost_nondep_bottom_3_quartiles_no_cc, depGroupVar) %>%
  mutate(depGroupVar = ifelse(depGroupVar == 1, "Non-depressed", "Depressed"))

@@

violin_mean_fascicle_volume_no_cc <- ggplot(df_mean_fascicle_volumes_and_diagnosis_no_cc, aes(x=depGroupVar, y=total_fascicle_vol_lost_no_cc, fill=depGroupVar)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  scale_x_discrete(labels=c("1" = "Depressed", "2" = "Non-Depressed")) + 
  ggtitle(paste0("Mean Fascicle Volume Affected by Diagnosis, No CC")) +
  ylab("Mean Volume of Fascicles") +
  ylim(0,42000) + 
  theme(plot.title = element_text(size=16, hjust = 0.55),
        axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
        axis.title.y = element_text(size=16),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
        legend.position = "none",
        aspect.ratio=7/5,
        panel.background = element_rect(colour = "white", fill = "white"))
print(violin_mean_fascicle_volume_no_cc) #p=0.067

violin_mean_fascicle_volume_dep <- ggplot(df_mean_fascicle_volumes_and_diagnosis, aes(x=depGroupVar, y=total_fascicle_vol_lost_indepnet_top_quartile, fill=depGroupVar)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  scale_x_discrete(labels=c("1" = "Depressed", "2" = "Non-Depressed")) + 
  ggtitle(paste0("Mean Fascicle Volume Affected Dep Net by Diagnosis")) +
  ylab("Mean Volume of Fascicles") +
  ylim(0,42000) + 
  theme(plot.title = element_text(size=16, hjust = 0.55),
        axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
        axis.title.y = element_text(size=16),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
        legend.position = "none",
        aspect.ratio=7/5,
        panel.background = element_rect(colour = "white", fill = "white"))
print(violin_mean_fascicle_volume_dep)

violin_mean_fascicle_volume_dep_no_cc <- ggplot(df_mean_fascicle_volumes_and_diagnosis_no_cc, aes(x=depGroupVar, y=total_fascicle_vol_lost_indepnet_top_quartile_no_cc, fill=depGroupVar)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  scale_x_discrete(labels=c("1" = "Depressed", "2" = "Non-Depressed")) + 
  ggtitle(paste0("Mean Fascicle Volume Affected Dep Net by Diagnosis")) +
  ylab("Mean Volume of Fascicles") +
  ylim(0,42000) + 
  theme(plot.title = element_text(size=16, hjust = 0.55),
        axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
        axis.title.y = element_text(size=16),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
        legend.position = "none",
        aspect.ratio=7/5,
        panel.background = element_rect(colour = "white", fill = "white"))
print(violin_mean_fascicle_volume_dep_no_cc)

violin_mean_fascicle_volume_nondep <- ggplot(df_mean_fascicle_volumes_and_diagnosis, aes(x=depGroupVar, y=total_fascicle_vol_lost_nondep_bottom_3_quartiles,  fill=depGroupVar)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  scale_x_discrete(labels=c("1" = "Depressed", "2" = "Non-Depressed")) + 
  ggtitle(paste0("Mean Fascicle Volume Affected Nondep Net by Diagnosis")) +
  ylab("Mean Volume of Fascicles") +
  ylim(0,42000) + 
  theme(plot.title = element_text(size=16, hjust = 0.55),
        axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
        axis.title.y = element_text(size=16),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
        legend.position = "none",
        aspect.ratio=7/5,
        panel.background = element_rect(colour = "white", fill = "white"))
print(violin_mean_fascicle_volume_nondep)

# geom violin within vs outside depression network
dep_net_group <- c(rep("Dep_net", times = 380), rep("Non_dep_net",times = 380))
net_values <- c(df_mean_fascicle_volumes_and_diagnosis$total_fascicle_vol_lost_indepnet_top_quartile, df_mean_fascicle_volumes_and_diagnosis$total_fascicle_vol_lost_nondep_bottom_3_quartiles)

newdf <- data.frame(dep_net_group, net_values)

#p = 2.2 x 10^-16. But it is kind of irrelevant because corpus callosum, which is periventricular and just so much bigger, is in the depression network so if you look at volume alone, there is really no way to compete. For this, you gotta use proportion. And when you drop the cranial nerves, doesn't work. COuld try dropping CC, but don't know why I coul dmake the case for that. Though honestly, will prob have to try
violin_within_vs_outside_network_fascicle_volume <- ggplot(newdf, aes(x=dep_net_group, y=net_values, fill=dep_net_group)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  scale_x_discrete(labels=c("1" = "Dep Net", "2" = "Non-Dep Net")) + 
  ggtitle(paste0("Mean Fascicle Volume Affected by Network")) +
  ylab("Mean Volume of Fascicles") +
  ylim(0,42000) + 
  theme(plot.title = element_text(size=16, hjust = 0.55),
        axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
        axis.title.y = element_text(size=16),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
        legend.position = "none",
        aspect.ratio=7/5,
        panel.background = element_rect(colour = "white", fill = "white"))
print(violin_within_vs_outside_network_fascicle_volume) #

# geom violin within vs outside depression network, no cc
dep_net_group <- c(rep("Dep_net", times = 380), rep("Non_dep_net",times = 380))
net_values <- c(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_vol_lost_indepnet_top_quartile_no_cc, dep_and_healthy_groups_for_ICD_analysis$total_fascicle_vol_lost_nondep_bottom_3_quartiles_no_cc)

newdf_no_cc <- data.frame(dep_net_group, net_values)

#p = 2.2 x 10^-16. But it is kind of irrelevant because corpus callosum, which is periventricular and just so much bigger, is in the depression network so if you look at volume alone, there is really no way to compete. For this, you gotta use proportion. And when you drop the cranial nerves, doesn't work. COuld try dropping CC, but don't know why I coul dmake the case for that. Though honestly, will prob have to try
violin_within_vs_outside_network_fascicle_volume_no_cc <- ggplot(newdf_no_cc, aes(x=dep_net_group, y=net_values, fill=dep_net_group)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  scale_x_discrete(labels=c("1" = "Dep Net", "2" = "Non-Dep Net")) + 
  ggtitle(paste0("Mean Fascicle Volume Affected by Network, no CC")) +
  ylab("Mean Volume of Fascicles") +
  ylim(0,42000) + 
  theme(plot.title = element_text(size=16, hjust = 0.55),
        axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
        axis.title.y = element_text(size=16),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
        legend.position = "none",
        aspect.ratio=7/5,
        panel.background = element_rect(colour = "white", fill = "white"))
print(violin_within_vs_outside_network_fascicle_volume_no_cc) #

### scaling by size of network

dep_net_group <- c(rep("Dep_net", times = 380), rep("Non_dep_net",times = 380))
net_values <- c(dep_and_healthy_groups_for_ICD_analysis$prop_fascicle_vol_lost_indepnet_top_quartile, dep_and_healthy_groups_for_ICD_analysis$prop_fascicle_vol_lost_bottom_3_quartile)

newdf_no_cc <- data.frame(dep_net_group, net_values)

#p = 2.2 x 10^-16. 
violin_within_vs_outside_network_scaled_by_network_size <- ggplot(newdf_no_cc, aes(x=dep_net_group, y=net_values, fill=dep_net_group)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  scale_x_discrete(labels=c("1" = "Dep Net", "2" = "Non-Dep Net")) + 
  ggtitle(paste0("Proportion Fascicle Volume Affected by Network")) +
  ylab("Proportion (tot volume lost/Net Vol) ") +
  ylim(0,0.1) + 
  theme(plot.title = element_text(size=16, hjust = 0.55),
        axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
        axis.title.y = element_text(size=16),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
        legend.position = "none",
        aspect.ratio=7/5,
        panel.background = element_rect(colour = "white", fill = "white"))
print(violin_within_vs_outside_network_scaled_by_network_size) #

@@

```{r age_effects_fascicles_unique_volume}
########### age effect whole group

#isolate out only the depressed group and healthy group
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicle_volumes_full %>% 
  filter(depGroupVar != 0)  %>% 
  mutate(total_fascicle_vol_lost = rowMeans(across(fascicle_names_no_cranial_nerves))) %>%
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup()

#### age histo ###
hist(dep_and_healthy_groups_for_ICD_analysis$PAT_AGE_AT_EXAM,
main = paste0("Age In Good Mimosa Group : n = ", dim(dep_and_healthy_groups_for_ICD_analysis)[1]), xlab = "Age", breaks = 10)

#lm
fascicle_age_lm <- lapply(fascicle_names_no_cranial_nerves, function(x) 
{
  lm(substitute(i ~ PAT_AGE_AT_EXAM, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
})
names(fascicle_age_lm) <- fascicle_names_no_cranial_nerves

#anova
fascicle_age_anova <- lapply(fascicle_age_lm, anova)

#fdr corrected
fascicle_age_anova_fdr <- fdr_anova_generic(fascicle_age_anova, 1)
print(fascicle_age_anova_fdr)

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_age_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

#visreg
#sapply(fascicle_age_lm,visreg)
visreg(fascicle_age_lm$AF_R,ylab = "Volume of Affected Streamlines", xlab = "Age in Years",
       line=list(col="red"),
       points=list(col="black"))

### Mean Volume loss x age
age_x_vol_affected <- lm(total_fascicle_vol_lost~ PAT_AGE_AT_EXAM, data=dep_and_healthy_groups_for_ICD_analysis )
print(summary(age_x_vol_affected))
visreg(age_x_vol_affected, gg=TRUE) + 
  xlab("Age") + 
  ylab("Mean Volume of Fascicle Affected") + 
  ggtitle("Mean Volume of Fascicles Affected by Age, p = 2.1*10^-5") + 
  theme(plot.title = element_text(hjust = 0.5))

scatter_age_x_vol_affected <- ggplot(data=age_x_vol_affected, aes(x=PAT_AGE_AT_EXAM, y=total_fascicle_vol_lost)) +
  geom_point(size=1) + 
  geom_smooth(method=lm)+
  xlab("Age") + 
  ylab("Mean Volume of Fascicles Affected") + 
  ggtitle("Mean Volume of Fascicles Affected by Age, p = 2.1*10^-5") + 
  theme(plot.title = element_text(hjust = 0.5, size=20),
        axis.title = element_text(size=20),
        axis.text = element_text(size=14),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
        panel.background = element_rect(colour = "white", fill = "white"))
print(scatter_age_x_vol_affected)

##### Ascending graph of all age regressions
#get lm results, including uncorrected
df_t_lm_age <- sapply(fascicle_age_lm, function(v) summary(v)$coefficients[2,3])

#Convert to data frame
df_t_lm_age <- data_frame(fascicle_names_no_cranial_nerves, df_t_lm_age)
names(df_t_lm_age) = c("Fascicle", "tvalue")

#remove items with cranial nerves
df_t_lm_age_no_cranial_nerves <- df_t_lm_age  %>% filter(Fascicle %in% fascicle_names_no_cranial_nerves)

df_t_lm_age_no_cranial_nerves$Fascicle <- factor(df_t_lm_age_no_cranial_nerves$Fascicle, levels = df_t_lm_age_no_cranial_nerves$Fascicle[order(df_t_lm_age_no_cranial_nerves$tvalue)])

# bar graph of T-values of fascicles
plot_fascicle_by_t_sorted <-ggplot(data = df_t_lm_age_no_cranial_nerves, aes(x = Fascicle, y=tvalue))+ 
  geom_bar(stat="identity") +
  xlab("Fascicle") + 
  ylab("T-value of AgexFascile Affected Regression") + 
  ylim(-2,8) +
  ggtitle("Effects of age within each fascicle ") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.title = element_text(hjust = 0.5, size=30),
        axis.title.x = element_text(size=30),
        axis.title.y = element_text(size=30))
print(plot_fascicle_by_t_sorted)
```
